---
title: "RQ 1"
output: html_document
date: "2023-12-06"
---

```{r, include = F}
knitr::opts_chunk$set(echo = TRUE)

set.seed(857287)

library(tidyverse)
library(oddsratio)
library(scales)
library(knitr)
library(kableExtra)
library(here)
library(MOTE)
`%+%` <- paste0

get_d <- function(x) {
  
  x1 <- df[[x]][df$self_id == T]
  x2 <- df[[x]][df$self_id == F]
  
  m1 <- mean(x1, na.rm = T)
  m2 <- mean(x2, na.rm = T)
  
  sd1 <- sd(x1, na.rm = T)
  sd2 <- sd(x2, na.rm = T)
  
  n1 <- sum(!is.na(x1))
  n2 <- sum(!is.na(x2))
  
  d <- d.ind.t(m1 = m1, m2 = m2, sd1 = sd1, sd2 = sd2, n1 = n1, n2 = n2)
  
  return(d$estimate)
  
}

df <- readRDS("H:\\My Drive\\Research\\Projects\\Autism Identification\\Data\\Analysis-Ready Data.rds")

p_values <- tibble()

## Recode variables as needed for pre-registered analyses
# Race/ethnicity
df$race_ethnicity_recoded = df$race_ethnicity == "White non-Hispanic"

# Education
df$education_recoded <- case_when(
  df$education %in% c("Less than a high school diploma", "High school degree or equivalent (e.g., GED, modified diploma, certificate of completion)") ~ 1,
  df$education == "Some college" ~ 2,
  df$education == "Associate degree (e.g., AA, AS)" ~ 3,
  df$education == "Bachelor’s degree (e.g., BA, BS)" ~ 4,
  df$education %in% c("Master’s degree (e.g., MA, MS)", "Professional or doctorate degree (e.g., MD, DDS, DVM, PhD, EdD, PsyD)") ~ 5,
  df$education == "Other:" ~ NA_real_
)

# Disability
df$disability <- as.character(df$disability)
df$disability[df$disability == "Prefer not to say"] <- NA

# Autism as disability
df$autism_dis <- as.character(df$autism_dis)
```

# Sample Description

```{r}
# Age
df %>%
  summarize(mean = mean(age, na.rm = T),
            sd = sd(age, na.rm = T)) %>%
  kable() %>%
  kable_styling()

# Gender
df %>%
  count(gender) %>%
  mutate(percent = percent(n / sum(n), .1)) %>%
  kable() %>%
  kable_styling()

# TGD gender breakdown
df %>%
  pivot_longer(matches("gender_[0-9]*$")) %>%
  count(value) %>%
  mutate(percent = percent(n / nrow(df), .1)) %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling()

# Sexuality
df %>%
  count(sexuality) %>%
  mutate(percent = percent(n / sum(n), .1)) %>%
  kable() %>%
  kable_styling()

# LGBQ+ breakdown
df %>%
  pivot_longer(matches("sexuality_[0-9]*$")) %>%
  count(value) %>%
  mutate(percent = percent(n / nrow(df), .1)) %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling()

# Race/ethnicity
df %>%
  count(race_ethnicity) %>%
  mutate(percent = percent(n / sum(n), .1)) %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling()

# Education
df %>%
  count(education) %>%
  mutate(percent = percent(n / sum(n), .1)) %>%
  kable() %>%
  kable_styling()

# Employment
df %>% 
  pivot_longer(starts_with("employment")) %>%
  group_by(name) %>%
  summarize(n = sum(value),
            percent = percent(n / nrow(df), .1)) %>%
  arrange(desc(n)) %>%
  kable() %>%
  kable_styling()
```

# RQ 1: Who self-identifies as autistic without a formal diagnosis?

## 1A. What demographic factors (age, gender, sexuality, race, employment, education) are associated with autism self-identification?

## 1B. What autistic traits (social interaction, communication, social camouflage, cognitive rigidity, repetitive behaviors, sensory sensitivity, speech, RAADS-14 score) are associated with autism self-identification?

## 1C. What psychosocial outcomes (depression, anxiety, disability, impairment, wellbeing, autism community belonging) are associated with autism self-identification?

## 1D. What support needs (current/past/unmet need of various support services) are associated with autism self-identification?

## 1E. What beliefs about autism (what defines “autism,” is it a disability) are associated with autism self-identification?

## 1F. What other aspects of a person’s autistic experience (age first aware, having autistic family or friends) are associated with autism self-identification?

### Tests of Continuous Outcomes

```{r, results = "asis"}
continuous_outcomes <- df %>%
  select(age,
         starts_with("cati"),
         raads_sum,
         phq_dep, 
         phq_anx,
         whodas_sum, 
         wemwbs_sum,
         matches("support_.*_total"),
         starts_with("asis"),
         age_first_aware) %>%
  names()

for(x in continuous_outcomes) {
  
  print(x)
  
  # Descriptive statistics
  df %>%
    group_by(self_id) %>%
    summarize(mean = mean(get(x), na.rm = T),
              sd = sd(get(x), na.rm = T)) %>%
    kable(caption = x) %>%
    kable_styling() %>%
    print()
  
  # Effect size
  get_d(x) %>%
    print()
  
  # Test
  x_by_id <- t.test(
    df[[x]] ~ df$self_id
  )
  
  statistic <- "t(" %+% round(x_by_id$parameter) %+% ") = " %+% round(x_by_id$statistic, 2)
  
  p_value <- x_by_id$p.value
  
  out <- tibble(
    name = x,
    statistic = statistic,
    p_value = p_value
  )
  
  p_values <- bind_rows(p_values, out)
  
}
```

### Tests of Nominal Outcomes

```{r, results = "asis"}
nominal_outcomes <- df %>%
  select(gender, 
         sexuality, 
         race_ethnicity_recoded,
         employment_employed, employment_unemployed, employment_unable,
         raads_cutoff, 
         disability, disability_autism,
         support_current_mental_health:support_need_health,
         autism_dis, 
         starts_with("fam"),
         starts_with("friend")) %>%
  names()

for(x in nominal_outcomes) {
  
  # Descriptive statistics
  df %>%
    group_by(self_id) %>%
    count(get(x)) %>%
    drop_na() %>%
    mutate(percent = percent(n / sum(n), .1)) %>%
    kable(caption = x) %>%
    kable_styling() %>%
    print()
  
  # Test
  x_by_id <- chisq.test(table(df$self_id, as.character(df[[x]])))
  
  statistic <- "X^2(" %+% round(x_by_id$parameter) %+% ") = " %+% round(x_by_id$statistic, 2)
  
  p_value <- x_by_id$p.value
  
  out <- tibble(
    name = x,
    statistic = statistic,
    p_value = p_value
  )
  
  p_values <- bind_rows(p_values, out)

}
```

### Tests of Ordinal Outcomes

```{r, results = "asis"}
ordinal_outcomes <- c("education_recoded", "speaking_now", "speaking_child")

for(x in ordinal_outcomes) {
  
  # Descriptive statistics
  df %>%
    group_by(self_id) %>%
    count(get(x)) %>%
    drop_na() %>%
    mutate(percent = percent(n / sum(n), .1)) %>%
    kable(caption = x) %>%
    kable_styling() %>%
    print()
  
  # Test
  x_by_id <- wilcox.test(as.numeric(df[[x]]) ~ df$self_id, na.rm = T, paired = F, exact = F)
  
  statistic <- "U = " %+% round(x_by_id$statistic, 2)
  
  p_value <- x_by_id$p.value
  
  out <- tibble(
    name = x,
    statistic = statistic,
    p_value = p_value
  )
  
  p_values <- bind_rows(p_values, out)

}
```

### Test Results

```{r}
p_values$p_adj <- p.adjust(p_values$p_value, "BH")

p_values %>% 
  kable() %>%
  kable_styling()
```

### Figures

Traits

```{r}
df %>%
  select(response_id, self_id, starts_with("cati"), raads_sum) %>%
  pivot_longer(
    c(starts_with("cati"), raads_sum)
  ) %>%
  drop_na() %>%
  group_by(self_id, name) %>%
  summarize(mean = mean(value),
            se = sd(value) / sqrt(n()),
            .groups = "drop") %>%
  mutate(ci_high = mean + (1.96 * se),
         ci_low = mean - (1.96 * se),
         name = recode_factor(
           name, 
           "cati_com" = "Communication",
           "cati_rep" = "Repetitive Behaviors",
           "cati_rig" = "Cognitive Rigidity",
           "cati_sen" = "Sensory Sensitivity",
           "cati_soc" = "Social Interactions",
           "cati_cam" = "Social Camouflage",
           "cati_sum" = "CATI Sum",
           "raads_sum" = "RAADS-14 Sum"
         )) %>%
  ggplot(aes(self_id, mean, group = self_id)) +
  geom_col(aes(fill = self_id), position = "dodge") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), position = position_dodge(.9), width = .25) +
  scale_x_discrete(name = "Group", labels = c("Diagnosis", "Self-ID")) +
  scale_y_continuous(name = "Mean") +
  scale_fill_discrete(name = "Group", labels = c("Diagnosis", "Self-ID")) +
  ggtitle("Autistic Traits by Group") +
  theme_classic() +
  theme(legend.position = "none") +
  facet_wrap(~ name, ncol = 4, scales = "free")

ggsave(filename = here("Figures", "Autistic Traits by Group.png"),
       width = 8,
       height = 5,
       units = "in")
```

Supports

```{r}
df %>%
  select(response_id, self_id, starts_with("support"), -ends_with("total")) %>%
  pivot_longer(
    starts_with("support")
  ) %>%
  group_by(self_id, name) %>%
  summarize(prop = mean(value),
            se = sd(value) / sqrt(n()),
            .groups = "drop") %>%
  mutate(ci_high = prop + (1.96 * se),
         ci_low = prop - (1.96 * se),
         vartype = case_when(
           grepl("current", name) ~ "Current",
           grepl("past", name) ~ "Past",
           grepl("need", name) ~ "Need"
         ) %>%
           factor(levels = c("Past", "Current", "Need")),
         support = name %>%
           gsub("^([^_]*_){2}", "", .) %>%
           recode_factor(
             "case_management" = "Case Management",
             "functional" = "Functional\n(e.g., Speech\nTherapy)",
             "health" = "Health\n(e.g., Specialized\nMedical Care)",
             "mental_health" = "Mental Health\n(e.g., Therapy)",
             "social" = "Social\n(e.g., Social\nSkills Training)",
             "vocational" = "Vocational\n(e.g., Job Training)"
           )) %>%
  ggplot(aes(support, prop, group = self_id)) +
  geom_col(aes(fill = self_id), position = "dodge") +
  geom_errorbar(aes(ymin = ci_low, ymax = ci_high), position = position_dodge(.9), width = .25) +
  scale_x_discrete(name = "Support Type") +
  scale_y_continuous(name = "Percent", labels = scales::percent) +
  scale_fill_discrete(name = "Group", labels = c("Diagnosis", "Self-ID")) +
  ggtitle("Support Access and Need by Group") +
  theme_classic() +
  facet_wrap(~ vartype, ncol = 1, scales = "free")

ggsave(filename = here("Figures", "Supports by Group.png"),
       width = 8,
       height = 5,
       units = "in")
```

PHQ-2

```{r}
dep_id <- df %>%
  filter(self_id == T) %>%
  drop_na(phq_dep) %>%
  pull(phq_dep)

dep_dx <- df %>%
  filter(self_id == F) %>%
  drop_na(phq_dep) %>%
  pull(phq_dep)

dep_norm <- tibble(
  phq_dep = 0:6,
  pr = c(24.3, 59.9, 80.9, 93.0, 96.8, 98.7, 99.6),
  radius = NA
)

for(i in 1:nrow(dep_norm)) {
  
  if(i == 1) {
    
    dep_norm$radius[i] <- dep_norm$pr[i] * 2
    
  } else {
    
    dep_norm$radius[i] <- (dep_norm$pr[i] - dep_norm$radius[i - 1]) + dep_norm$pr[i]
    
  }
  
}

dep_norm <- dep_norm %>%
  mutate(
    radius_lag = lag(radius, 1, default = 0),
    pr_size = radius - radius_lag,
    n = pr_size * 10
  )

dep_norm_temp <- rep(dep_norm$phq_dep, dep_norm$n)

bind_rows(
  tibble(group = "Autistic: Diagnosed", phq_dep = dep_dx), 
  tibble(group = "Autistic: Self-Identify", phq_dep = dep_id),
  tibble(group = "General Population", phq_dep = dep_norm_temp)
) %>%
  ggplot() +
  geom_density(aes(phq_dep, group = group, fill = group), alpha = .25, bw = 1) +
  scale_x_continuous(name = "PHQ-2 Sum Score") +
  scale_y_continuous(name = "Density", labels = scales::percent) +
  scale_fill_discrete(name = "Group") +
  ggtitle("Depression Symptom Severity by Group") +
  theme_classic()

ggsave(filename = here("Figures", "Depression by Group.png"),
       width = 6,
       height = 4,
       units = "in")
```

GAD-2

```{r}
anx_id <- df %>%
  filter(self_id == T) %>%
  drop_na(phq_anx) %>%
  pull(phq_anx)

anx_dx <- df %>%
  filter(self_id == F) %>%
  drop_na(phq_anx) %>%
  pull(phq_anx)

anx_norm <- tibble(
  phq_anx = 0:6,
  pr = c(28.2, 66.4, 83.9, 93.5, 96.8, 98.5, 99.5),
  radius = NA
)

for(i in 1:nrow(anx_norm)) {
  
  if(i == 1) {
    
    anx_norm$radius[i] <- anx_norm$pr[i] * 2
    
  } else {
    
    anx_norm$radius[i] <- (anx_norm$pr[i] - anx_norm$radius[i - 1]) + anx_norm$pr[i]
    
  }
  
}

anx_norm <- anx_norm %>%
  mutate(
    radius_lag = lag(radius, 1, default = 0),
    pr_size = radius - radius_lag,
    n = pr_size * 10
  )

anx_norm_temp <- rep(anx_norm$phq_anx, anx_norm$n)

bind_rows(
  tibble(group = "Autistic: Diagnosed", phq_anx = anx_dx), 
  tibble(group = "Autistic: Self-Identify", phq_anx = anx_id),
  tibble(group = "General Population", phq_anx = anx_norm_temp)
) %>%
  ggplot() +
  geom_density(aes(phq_anx, group = group, fill = group), alpha = .25, bw = 1) +
  scale_x_continuous(name = "GAD-2 Sum Score") +
  scale_y_continuous(name = "Density", labels = scales::percent) +
  scale_fill_discrete(name = "Group") +
  ggtitle("Anxiety Symptom Severity by Group") +
  theme_classic()

ggsave(filename = here("Figures", "Anxiety by Group.png"),
       width = 6,
       height = 4,
       units = "in")
```

WEMWBS

```{r}
wemwbs_id <- df %>%
  filter(self_id == T) %>%
  drop_na(wemwbs_sum) %>%
  pull(wemwbs_sum)

wemwbs_dx <- df %>%
  filter(self_id == F) %>%
  drop_na(wemwbs_sum) %>%
  pull(wemwbs_sum)

wemwbs_norm <- rnorm(1000, 51.607, 8.706)

bind_rows(
  tibble(group = "Autistic: Diagnosed", wemwbs = wemwbs_dx), 
  tibble(group = "Autistic: Self-Identify", wemwbs = wemwbs_id),
  tibble(group = "General Population", wemwbs = wemwbs_norm)
) %>%
  ggplot() +
  geom_density(aes(wemwbs, group = group, fill = group), alpha = .25, bw = 5) +
  scale_x_continuous(name = "WEMWBS Sum Score") +
  scale_y_continuous(name = "Density", labels = scales::percent) +
  scale_fill_discrete(name = "Group") +
  ggtitle("Well-Being by Group") +
  theme_classic()

ggsave(filename = here("Figures", "Well-Being by Group.png"),
       width = 6,
       height = 4,
       units = "in")
```

### Follow-Up: Outcomes by Support Need

```{r}
library(yhat)

# Anxiety
lm(
  data = df,
  formula = phq_anx ~ self_id
) %>%
  summary()

lm(
  data = df,
  formula = phq_anx ~ self_id + support_need_total
) %>%
  summary()

commonality(
  aps(
    dataMatrix = df,
    dv = "phq_anx",
    ivlist = c("self_id", "support_need_total")
  )
) %>%
  kable() %>%
  kable_styling()

# Wellbeing
lm(
  data = df,
  formula = wemwbs_sum ~ self_id
) %>%
  summary()

lm(
  data = df,
  formula = wemwbs_sum ~ self_id + support_need_total
) %>%
  summary()

commonality(
  aps(
    dataMatrix = df,
    dv = "wemwbs_sum",
    ivlist = c("self_id", "support_need_total")
  )
) %>%
  kable() %>%
  kable_styling()
```

### Equivalence Testing

```{r}
# MOTE::d.ind.t(m1 = id_mean, m2 = dx_mean, sd1 = id_sd, sd2 = dx_sd, n1 = sum(df$self_id), n2 = sum(!df$self_id))
# 
# TOSTER::tsum_TOST(m1 = id_mean, m2 = dx_mean, sd1 = id_sd, sd2 = dx_sd, n1 = sum(df$self_id), n2 = sum(!df$self_id),
#                   hypothesis = "EQU",
#                   paired = F,
#                   var.equal = F,
#                   eqb = .3,
#                   alpha = .025, #The only difference between this and the MOTE version is this uses two one-tailed tests, and so relies on a 90% CI if the alpha = .05
#                   eqbound_type = "SMD")


```